### 2018-01-16 Paper/jaccardbaetica.tex
add paper jaccard

\subsection{Baetica province}

hola

>>>>

We analysed a dataset of 131 stamps from 81 workshops. All the dataset was collected from CEIPAC database (citar). The workshops were located in Baetica area along the river Guadalquivir and its tributary Genil.

\subsection{Jaccard distance}
%%usar Jaccard disimilarity and similarity

The dataset was analysed using a statistic method as Jaccard index. Jaccard distance was used to calculate the distance among the stamps.
